${toc}

```{r echo = FALSE, include = F}
library(knitr)
knitr::read_chunk("knitr_chunks.R")
```

```{r setup, echo = FALSE, include = F}
```

```{r validation3, echo = FALSE, include = F}
```

# TCR binding by flow (WashU)
This assay is a cytometry-based tetramer screen. See more details at Consortium Validation Page. Data is shown for top 20 ranked peptides only.

## Number of tested peptides
```{r plot1, echo = F, warning=F, fig.width = 20, fig.height = 10}
make_validated_submissions_boxplot(validation_df, "TCR_FLOW_I", "COUNT", "Number of tested peptides")
```


## Mean rank of tested peptides
```{r plot2, echo = F, warning=F, fig.width = 20, fig.height = 10}
make_validated_submissions_boxplot(validation_df, "TCR_FLOW_I", "MEAN_RANK", "Mean rank of tested peptides")
```


## Validation rate of tested peptides
```{r plot3, echo = F, warning=F, fig.width = 20, fig.height = 10}
make_validated_submissions_boxplot(validation_df, "TCR_FLOW_I", "RATE", "Validation rate of tested peptides")
```

# T cell reactivity screen (Mt. Sinai)

An in vitro functional assay for T cell proliferation. See more details at Consortium Validation Page. Data is shown for top 20 ranked peptides only.

## Number of tested peptides
```{r plot10, echo = F, warning=F, fig.width = 20, fig.height = 10}
make_validated_submissions_boxplot(validation_df, "TCELL_REACTIVITY", "COUNT", "Number of tested peptides")
```


## Mean rank of tested peptides
```{r plot11, echo = F, warning=F, fig.width = 20, fig.height = 10}
make_validated_submissions_boxplot(validation_df, "TCELL_REACTIVITY", "MEAN_RANK", "Mean rank of tested peptides")
```


## Validation rate of tested peptides
```{r plot12, echo = F, warning=F, fig.width = 20, fig.height = 10}
make_validated_submissions_boxplot(validation_df, "TCELL_REACTIVITY", "RATE", "Validation rate of tested peptides")
```
