${toc}

```{r setup, echo = FALSE, include = F}
library(knitr)
library(yaml)
library(tidyverse)
library(magrittr)
library(synapser)

synLogin()

config <- read_yaml("config.yaml")
round <- "1"
CURRENT_TEAM <- config$team

source("markdown_functions.R")
source("plot_functions.R")
source("query_functions.R")

knitr::read_chunk("knitr_chunks.R")

```

```{r variant overlap, echo = FALSE, include = F}
```
Submitted VCFs were sorted compared using bcftools stats. We then extracted the variants used to predict the top 20 peptides. For each combination of team A and team B, the overlap of these variants was calculated as: intersect(A,B) / length(A). Then for each team, the median was calculated across all comparisons of that team with other teams. Your team's value is shown by a red dot.

# Patient 1
```{r echo = F, warning=F, fig.width = 20, fig.height = 10}
text <- make_variant_histogram("1", variant_overlap_df)
```
`r text`

# Patient 2
```{r echo = F, warning=F, fig.width = 20, fig.height = 10}
text <- make_variant_histogram("2", variant_overlap_df)
```
`r text`

# Patient 3
```{r echo = F, warning=F, fig.width = 20, fig.height = 10}
text <- make_variant_histogram("3", variant_overlap_df)
```
`r text`

# Patient 4
```{r echo = F, warning=F, fig.width = 20, fig.height = 10}
text <- make_variant_histogram("4", variant_overlap_df)
```
`r text`