${toc}

```{r echo = FALSE, include = F}
library(knitr)
knitr::read_chunk("knitr_chunks.R")
```

```{r setup, echo = FALSE, include = F}
```

```{r validation1, echo = FALSE, include = F}
```

# Predicted and measured binding values for peptides tested thus far.
Values are shown for peptides predicted by your team, as well as values predicted for those same peptides by other teams, and the measured binding values.

For a given allele, the absence of a plot implies none of your teams predicted neoepitopes for that allele were validated.


## A*01:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("A*01:01", dotplot_df)
```
`r text`

## A*02:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("A*02:01", dotplot_df)
```
`r text`

## A*03:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("A*03:01", dotplot_df)
```
`r text`

## A*32:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("A*32:01", dotplot_df)
```
`r text`

## A*68:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("A*68:01", dotplot_df)
```
`r text`

## B*07:02
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("B*07:02", dotplot_df)
```
`r text`

## B*08:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("B*08:01", dotplot_df)
```
`r text`

## B*44:02
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("B*44:02", dotplot_df)
```
`r text`

## B*51:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("B*51:01", dotplot_df)
```
`r text`

## B*57:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("B*57:01", dotplot_df)
```
`r text`

## C*03:03
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("C*03:03", dotplot_df)
```
`r text`

## C*05:01
```{r echo = F, fig.width = 20, fig.height = 10}
text <- make_dotplot("C*05:01", dotplot_df)
```
`r text`
